Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
replace s by z in g4
nudges

In order to exploit the full potential of the present approach, a
dynamical plant that can present physical components must be
considered.  However, a discrete plant model can also demonstrate some
benefits of the present approach, which considers FWL effects in the
digital controller implementation.  In particular, a classical cruise
control example is extracted from the literature~\cite{Astrom08},
where the discrete plant model (with time step of $0.2$s) is
represented by the following z-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
has designed a high-performance controller, which is characterised by the
following z-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$ (Eq.~\eqref{Eq:running-example-plant}) 
stabilizes the closed-loop system for the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}).  
However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16}
implementation format ({\it i.e.}, $4$ bits for the integer part and $16$
bits for the fractional part) can be represented by the following
expression:
%
\begin{equation}
\label{Eq:running-example-controller-quantised}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594},
\end{equation} 
%
which makes the system unstable in closed-loop using fixed-point arithmetic
and the typical series loop configuration, where $C_{q}\left(z\right)$ and
$G\left(z\right)$ are in the forward path.

\subsubsection{Program synthesis for the illustrative example}
We will illustrate our synthesis approach on the running example
described in the previous section. 
%in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
$$

In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:

$$
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}
$$

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
$$

This time the {\sc uncertainty} check doesn't find any more counterexamples 
and we pass the current candidate solution to the {\sc precision} verification stage.
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
We obtain the result $false$, meaning that the current precision is insufficient.
Consequently, we increase our precision to $I_b=20,F_b=28$.
%
Since the previous counterexamples were attained at lower precision, we
remove them from the counterexample set.  Back in the {\sc synthesise}
phase, we re-start the process with a candidate solution with all
coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}
$$

%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
In the next {\sc synthesise} phase, we get a new candidate solution that holds for
the new, higher precision counterexample:

$$
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

>>>>

In order to exploit the full potential of the present approach, a
dynamical plant that can present physical components must be
considered.  However, a discrete plant model can also demonstrate some
benefits of the present approach, which considers FWL effects in the
digital controller implementation.  In particular, a classical cruise
control example is extracted from the literature~\cite{Astrom08},
where the discrete plant model (with a time step of $0.2$s) is
represented by the following $z$-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16}
has designed a high-performance controller, which is characterised by the
following $z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$
(Eq.~\eqref{Eq:running-example-plant}) stabilizes the closed-loop system for
the discrete plant model $G(z)$ (Eq.~\ref{Eq:running-example-controller}). 
However, if implementation aspects are considered during verification (e.g.,
fixed-point arithmetic and word-length), then this closed-loop system
becomes unstable.
%
For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as follows:
%
\begin{equation}
\label{Eq:running-example-controller-quantised}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594} \;.
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$C_{q}\left(z\right)$ and $G\left(z\right)$ are in the forward path, is
unstable.

\subsection{Program synthesis for the example}

We will illustrate our synthesis approach on the running example
described in the previous section. 
%in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
$$

In the first {\sc verify} stage, the {\sc uncertainty} 
check finds the following counterexample:
%
$$
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}
$$

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise}
phase, where we get the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
$$

This time, the {\sc uncertainty} check does not find any more
counterexamples and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_b=20$, $F_b=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the counterexample set.  Back in the {\sc synthesise}
phase, we re-start the process with a candidate solution with all
coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}
$$

In the next {\sc synthesise} phase, we get a new candidate solution that
eliminates the new, higher precision counterexample:
%
$$
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$
